Discrete Quantum Theories and Computing

### 2018-11-18 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating...

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections
of uncertain events \cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}.
Given a finite sample space~$\Omega$ representing all possible outcomes,
and its power set $2^{\Omega}$ as the classical event space, a classical
probability measure~$\mu$ maps an event~$E$ to a number $\mu\left(E\right)\in\left[0,1\right]$
specifying how likely one of the outcome in $E$ actually happens.
To maintain the coherence, we want $\mu$ subject to the following
constraints: $\mu\left(\emptyset\right)=0$, $\mu\left(\Omega\right)=1$,
$\mu\left(\overline{E}\right)=1-\mu\left(E\right)$, and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.

>>>>

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections
of uncertain events \cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}.
Given a finite sample space~$\Omega$ representing all possible outcomes,
and its power set $2^{\Omega}$ as the classical event space, a classical
probability measure~$\mu$ maps an event~$E$ to a number $\mu\left(E\right)\in\left[0,1\right]$
specifying how likely one of the outcome in $E$ actually happens.
To maintain the coherence, we want $\mu$ subject to the following
constraints. When $E$ contains no outcome, $E$ is the least likely
to happen, i.e., $\mu\left(\emptyset\right)=0$. When $E$ contains
all outcomes, $E$ is the most likely to happen, i.e., $\mu\left(\Omega\right)=1$.
If we know the likelihood of an event, $\mu\left(E\right)$, it is
natural to assume the likelihood of the event’s complement is just
the opposite of $\mu\left(E\right)$, i.e., $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$.
For each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$,
the likelihood of the union event is additive, $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$.

The previous abstraction
